Reproducible Research: A Tutorial on how to do the same thing more than once in R

### 2021-08-04 install.Rmd
add rtools
update required dependencies and advice windows users closes #140

1. Open a new terminal (Press Windows key + X, click on "Windows Powershell (Admin)").
2. Paste `choco install -y r r.studio`
3. Press enter

@@

Please note that Docker does not work on Windows 10 Home, you need Windows Pro or Education.

1. Open a new terminal (Press Windows key + X, click on "Windows Powershell (Admin)").
2. Paste `choco install -y git make docker`
3. Press enter.

>>>>

1. Open a new terminal (Press Windows key + X, click on "Windows Powershell (Admin)").
2. Paste `choco install -y r r.studio rtools`
3. Press enter

@@

Please note that Docker does may not work on Windows 10 Home, because Docker requires a feature called virtualization which you may have to enable. In that case follow this [guide](https://docs.docker.com/docker-for-windows/troubleshoot/#virtualization). This feature is usually enabled in Windows Pro or Education.
On Windows Home, you also require the Windows Subsystem for Linux (WSL) as well as the WSL Ubuntu extension.

1.  Open a new terminal (Press Windows key + X, click on “Windows
    Powershell (Admin)”).
2.  Paste `choco install -y git make docker`
3.  Press enter.

On Windows Home and systems without Hyper V:

1. Open a new terminal (Press Windows key + X, click on “Windows
    Powershell (Admin)”).
2. Paste `choco install -y git make docker wsl`
3. Press enter.
4. Restart.
5. Open a new terminal (Press Windows key + X, click on “Windows 
    Powershell (Admin)”).
6. Paste `choco install -y wsl-ubuntu-2004`
7. Press enter.

### 2021-08-04 manuscript.Rmd
add keywords
update required dependencies and advice windows users closes #140

**Docker** is a popular tool for containerization.
It manages software dependencies by constructing a virtual software environment independent of the host software environment.
These so-called "Docker images" function like a virtual computer  (i.e., a sort of "sand box").
A Docker image should contain *all* software dependencies used in an analysis - not just R-packages, but also R and Rstudio, and even the computer's operating system.
This is important because some of its functionality may impact the workings of higher-order software like R, such as calls to random number generators, linear algebra libraries and such within R.

@@

This tutorial assumes that the user is working predominantly in R, with the help of RStudio.
It describes basic steps that we expect to apply to all users. Your specific situation might involve additional, more specialized steps. After completing the tutorial, you should be able to customize your workflow accordingly.
The first step is to install the required software.
We assume that you have installed R and RStudio already but the tutorial will guide you in detail through the installation of other necessary software with the help of the R package [`repro`](https://github.com/aaronpeikert)[@R-repro].
In case you either have not installed R and RStudio or are unsure if they are up to date you might want to consult our installation advice in the [Online Supplementary Material](https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md) that covers how to install all software necessary for this tutorial in three steps.
Start R Studio and install the package [`repro`](https://github.com/aaronpeikert)[@R-repro]. 
It will assist you while you follow the tutorial.

>>>>

**Docker** is a popular tool for containerization.
It manages software dependencies by constructing a virtual software environment independent of the host software environment.
These so-called "Docker images" function like a virtual computer  (i.e., a sort of "sand box").
A Docker image should contain *all* software dependencies used in an analysis---not just R-packages, but also R and Rstudio, and even the computer's operating system.
This is important because some of its functionality may impact the workings of higher-order software like R, such as calls to random number generators, linear algebra libraries and such within R.

@@

This tutorial assumes that the user is working predominantly in R, with the help of RStudio.
It describes basic steps that we expect to apply to all users. Your specific situation might involve additional, more specialized steps. After completing the tutorial, you should be able to customize your workflow accordingly.
The first step is to install the required software.
We assume that you have installed R [@R-base, version `r with(R.version, paste0(major, ".", minor))`] and RStudio [@rstudio, version 1.4] already but the tutorial will guide you in detail through the installation of other necessary software with the help of the R package [`repro`](https://github.com/aaronpeikert)[@R-repro].
In case you either have not installed R and RStudio or are unsure if they are up to date you might want to consult our installation advice in the [Online Supplementary Material](https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md) that covers how to install all software necessary for this tutorial in three steps.
The [installation advice]((https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md)) may also help Windows users who have problems installing Docker.
Start R Studio and install the package [`repro`](https://github.com/aaronpeikert)[@R-repro]. 
It will assist you while you follow the tutorial.
